Multi-level modeling with Openflexo/\FML

### 2022-03-11 3-introduction.tex
cite LIMM paper (icse2011-limm) in the list of multi-level modeling approaches and tools

In order to tackle this problem, the \emph{multi-level} modeling paradigm has been introduced. Contrary to the strict approach, multi-level modeling advocates the use of a flexible number of levels as well as more flexible relations between them{\color{red} The article of ICSE by me and Fabien can be cited here}. This paradigm is gaining traction within the modeling community as evidenced by the contribution of many new multi-level modeling approaches and tools such as Melanee~\parencite{melanee}, MetaDepth~\parencite{metadepth}, MultEcore~\parencite{multecore2016}, DeepTelos~\parencite{deeptelos2016} or DMLA~\parencite{dmla2017}. Taking advantage of this vibrant state of affairs, and in order to foster discussion and enable comparison between competing approaches, a multi-level modeling challenge has been created for the MULTI workshop. This paper is a response to the latest multi-level modeling challenge~\parencite{multiProcessChallenge-emisaj}
%\footnote{It can be found here: \url{http://purl.org/emisajchallenge}. It is an updated version of the challenge used in~\textcite{multiProcessChallenge2019}}
which consists in providing a solution to the problem of specifying and enacting processes. Solutions to the \emph{Multi-level Process Challenge} must fulfill a number of requirements for a process representation defined at an abstract process-definition level and at various more concrete domain-specific levels, resulting in a multi-level hierarchy of related models. In this article, we respond to this challenge using a solution based on model federation~\parencite{Golra2016-federation}.

>>>>

In order to tackle this problem, the \emph{multi-level} modeling paradigm has
been introduced. Contrary to the strict approach, multi-level modeling
advocates the use of a flexible number of levels as well as more flexible
relations between them. %{\color{red} The article of ICSE by me and Fabien can be
%cited here} {(JC) \color{pink} Effectivement. intégré dans la liste}
This paradigm is gaining traction within the modeling community as evidenced by
the contribution of many new multi-level modeling approaches and tools such as
Melanee~\parencite{melanee}, LIMM~\parencite{icse2011-limm},
MetaDepth~\parencite{metadepth}, MultEcore~\parencite{multecore2016},
DeepTelos~\parencite{deeptelos2016} or DMLA~\parencite{dmla2017}. Taking
advantage of this vibrant state of affairs, and in order to foster discussion
and enable comparison between competing approaches, a multi-level modeling
challenge has been created for the MULTI workshop. This paper is a response to
the latest multi-level modeling challenge~\parencite{multiProcessChallenge-emisaj}
%\footnote{It can be found here: \url{http://purl.org/emisajchallenge}. It is an updated version of the challenge used in~\textcite{multiProcessChallenge2019}}
which consists in providing a solution to the problem of specifying and
enacting processes. Solutions to the \emph{Multi-level Process Challenge} must
fulfill a number of requirements for a process representation defined at an
abstract process-definition level and at various more concrete domain-specific
levels, resulting in a multi-level hierarchy of related models. In this
article, we respond to this challenge using a solution based on model
federation~\parencite{Golra2016-federation}.
